Experiment 2

### 2021-06-30 experiments/experiment 1/experiment 1.Rmd
run two experiments

---
title: "Experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output: html_document
---

@@

knitr::opts_knit$set(progress = TRUE, verbose = TRUE, cache = TRUE)

@@

library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("simulations/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
```

@@

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -5
SB_var_range <- 0.015789474
SB_var_TO <- -20.5
PB_var_range <- 0.015789474
PB_var_TO <- -20.5

@@

```{r}
default_sim_duration <- 100000
```

```{r}
default_minimum_abundances <- rep(1000, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB") 
```

```{r}
sim_number <- 1
default_log10a_series <- c(-1, -6, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

@@

```{r}
options(mc.cores = 8)
```

```{r}
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 20 ## number of a_0 values
a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

```{r}
var_expt <- run_ss_var_experiment()
```

```{r}
result_index1 <- 1
p1  <- plot_ss_result1(var_expt,
                result_index = result_index1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

>>>>

---
title: "Experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output: 
  html_document: 
    keep_md: yes
---

@@

knitr::opts_knit$set(progress = TRUE, verbose = FALSE, cache = TRUE)

@@

library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
```

@@

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474
CB_h_div <- -0.08
SB_gmax_div <- 0.015789474
SB_h_div <- -0.323
PB_gmax_div <- 0.015789474
PB_h_div <- -0.323

@@

```{r}
default_sim_duration <- 1000000
```

```{r}
default_minimum_abundances <- rep(100, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB") 
```

```{r}
sim_number1 <- 1
default_log10a_series <- c(-1, -8, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r}
sim_number2 <- 2
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r}
options(mc.cores = 6)
```

```{r}
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 1000 ## number of a_0 values
a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

result_index1 <- 1
p1  <- plot_ss_result1(var_expt,
                result_index = result_index1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

### 2021-06-30 experiments/experiment 2/experiment 2.Rmd
run two experiments

# devtools::install_github("opetchey/microxanox",
#                              ref="main",
#                              auth_token = "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",
#                              build_vignettes = FALSE,
#                              force = TRUE)

>>>>

devtools::install_github("opetchey/microxanox",
                             ref="main",
                             auth_token = "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",
                             build_vignettes = FALSE,
                             force = TRUE)
